### 2015-07-02 narrative/intro.tex
use case
modified:   bib/maltzahn.bib 	modified:   narrative/intro.tex

In this project we will extend ADIOS~\cite{adios} with new APIs and novel techniques
to coordinate with the storage back-end. The key idea is offering the ability to
negotiate with the storage system to agree on the tradeoff between data quality
and response time. We will test our ideas on the next generation OLCF,
SNL/LANL, and NERSC systems.
%
We plan to leverage the many inovations we discovered in 
the Lightweight File Systems~\cite{lwfs} (LWFS) project.
In this project, Sandia sought to
demonstrate stripping down a file system to the bare minimum features required
for any storage system. Then, additional functionality and semantics, such as
POSIX-style directories and consistency requirements, were added in using
auxiliary services separate from the stack or by layering providing a new
interface to the storage system. The project's first phase demonstrated that
using a core object storage system with integrated security providing
authentication and authorization services, customized storage interfaces could
be developed with exactly the overhead required for different applications. The
second phase of LWFS, known as Sirocco~\cite{sirocco}, is investigating how to
manage storage devices for efficient and scalable storage performance.  Sirocco
has been in process for three years and has developed a usable storage infrastructure.

>>>>

In this project we will extend ADIOS~\cite{adios} with new APIs and novel techniques
to coordinate with the storage back-end. The key idea is offering the ability to
negotiate with the storage system to agree on the tradeoff between data quality
and response time. We will test our ideas on the next generation OLCF,
SNL/LANL, and NERSC systems.
%
We plan to leverage the many inovations we discovered in 
the Lightweight File Systems~\cite{lwfs} (LWFS) project and the Ceph storage system project (ceph.com).
In the LWFS project, Sandia sought to
demonstrate stripping down a file system to the bare minimum features required
for any storage system. Then, additional functionality and semantics, such as
POSIX-style directories and consistency requirements, were added in using
auxiliary services separate from the stack or by layering providing a new
interface to the storage system. The project's first phase demonstrated that
using a core object storage system with integrated security providing
authentication and authorization services, customized storage interfaces could
be developed with exactly the overhead required for different applications. The
second phase of LWFS, known as Sirocco~\cite{sirocco}, is investigating how to
manage storage devices for efficient and scalable storage performance.  Sirocco
has been in process for three years and has developed a usable storage infrastructure.

The Ceph project (ceph.com) started at UC Santa Cruz in 2004 and
was initially funded by DOE/NNSA involving LLNL, LANL, and Sandia,
with the goal to create an object-based parallel file system that
addresses the well-known metadata service bottleneck of creating
and accessing 1000s of files comprising a checkpoint~\cite{weil:osdi06}.
However, after the Ceph kernel client was pulled into the Linux
mainline in 2010, the focus of Ceph shifted to its object-based
storage subsystem, also called Reliable Autonomous Distributed
Object Store (RADOS), which now is the dominant storage system in
OpenStack production-level deployments and was recently selected
as the new backend for Flickr and Yahoo! Cloud Services. In this
project we will leverage two of the key innovations of Ceph: (1)
Controlled Replication Under Scalable Hashing (CRUSH)~\cite{weil:sc06}
will help making resource identification and predictable performance
scalable, and (2) extensible storage object classes~\cite{watkins:ucsctr15}
will provide the main mechanisms of introducing new APIs,
metadata vocabulary, and quality of service into the storage stack.
